### 2013-08-03 exact_learning/paper.tex
fixing references to equations and figures

For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss-based soft-margin objective
\begin{equation}\label{mainequation}
\min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is a hinge-loss-like upper
bound on the empirical $\Delta$-risk:
\[r_i(x^i, y^i, y) = \left [\max_{y \in \mathcal{Y}} \Delta(y^i, y) + \left<\theta, \psi(x^i, y) - \psi(x^i, y^i) \right > \right]_+ \]

We solve the following reformulation of Equation~\ref{mainequation}, known as one-slack QP formulation:
\begin{align}\label{oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i,
            \hat{y}^i)] \right \rangle \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
using the cutting plane method described in
Algorithm~\ref{alg_cutting_plane}~\citep{joachims2009cutting}.

@@

\subsection{Bounding the Objective}\label{bounds}
Even using approximate inference procedures, several statements
about the original exact objective (Equation~\ref{mainequation}) can be
obtained.

@@

To determine whether to produce inference results from the cache or to run the inference algorithm,
we solve the QP once with a constraint from the cache. If the resulting $o^C$ verifies
\begin{equation}\label{cache_test}
    o^C - o^Q < \frac{1}{2} (o^Q - o_{\W})
\end{equation}
we continue using the caching oracle. Otherwise we run the inference algorithm again.
For testing \eqref{cache_test}, the last known value of $o^Q$ is used, as recomputing it would defy
the purpose of the cache.

>>>>

For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss-based soft-margin objective
\begin{equation}\label{eq:mainequation}
\min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is a hinge-loss-like upper
bound on the empirical $\Delta$-risk:
\[r_i(x^i, y^i, y) = \left [\max_{y \in \mathcal{Y}} \Delta(y^i, y) + \left<\theta, \psi(x^i, y) - \psi(x^i, y^i) \right > \right]_+ \]

We solve the following reformulation of Equation~\eqref{mainequation}, known as one-slack QP formulation:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i,
            \hat{y}^i)] \right \rangle \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
using the cutting plane method described in
Algorithm~\ref{alg_cutting_plane}~\citep{joachims2009cutting}.

@@

\subsection{Bounding the Objective}\label{bounds}
Even using approximate inference procedures, several statements
about the original exact objective (Equation~\eqref{mainequation}) can be
obtained.

@@

To determine whether to produce inference results from the cache or to run the inference algorithm,
we solve the QP once with a constraint from the cache. If the resulting $o^C$ verifies
\begin{equation}\label{eq:cache_test}
    o^C - o^Q < \frac{1}{2} (o^Q - o_{\W})
\end{equation}
we continue using the caching oracle. Otherwise we run the inference algorithm again.
For testing \eqref{cache_test}, the last known value of $o^Q$ is used, as recomputing it would defy
the purpose of the cache.
